\begin{thebibliography}{100} % 100 is a random guess of the total number of 
%references 

\bibitem{AHONEN04} Ahonen T., Hadid A., Pietikäinen M., \emph{Face Recognition with Local Binary Patterns}, Computer Vision - ECCV, 2004, Pages 469-481

\bibitem{AJANKI07} Ajanki A., \emph{Example of k-nearest neighbour classification}, 2007, http://commons.wikimedia.org/wiki/File:KnnClassification.svg [dostęp: 23.09.2014]

\bibitem{MARKETING12} Baier D., Daniel I., Frost S., \emph{Image data analysis and classification in marketing}, Advances in Data Analysis and Classification , Volume 6, Issue 4 , December 2012, Pages 253-276, ISSN 1862-5347

\bibitem{BAY08} Bay H., Ess A., Tuytelaars T., Van Gool L., \emph{SURF: Speeded Up Robust Features},  Computer Vision and Image Understanding (CVIU), Vol. 110, No. 3, 2008, Pages 346-359 

\bibitem{BISHOP06} Bishop C. M., \emph{Pattern Recognition and Machine Learning}, New York: Springer, 2006, ISBN 0-387-31073-8

\bibitem{CASEY} Casey C., \emph{Part Two: Like it or Not, Predictive Coding is Here and Judges Want you to Use it}, Hudson Legal Blog, 2012, http://us.hudson.com/legal/blog/postid/537/part-2 [dostep: 26.08.2014]

\bibitem{CHEN04} Chen Y., Wang J. Z., \emph{Image Categorization by Learning and Reasoning with Regions}, The Journal of Machine Learning Research, Volume 5, 2004, Pages 913-939 

\bibitem{CICHOSZ00} Cichosz P., \emph{Systemy uczące się}, Warszawa: Wydawnictwo Naukowo-Techniczne, 2000, ISBN 83-204-2544-1

\bibitem{DAI10} Dai D., Wu T., Zhu S-c., \emph{Discovering Scene Categories by Information Projection and Cluster Sampling}, CVPR 2010

\bibitem{DALAL05} Dalal N., Triggs B., \emph{Histograms of oriented gradients for human detection}, CVPR 2005, Volume 1, Pages 886 - 893 

\bibitem{DIETTERICH94} Dietterich T.G., Bakiri G., \emph{Solving multiclass learning problems via error-correcting output codes}, Journal of Artificial Intelligence Research, Volume 2 Issue 1, August 1994, Pages 263-286 

\bibitem{DUAN05} Duan K. B., Keerthi S. S., \emph{Which Is the Best Multiclass SVM Method? An Empirical Study}, Multiple Classifier Systems. Lecture Notes in Computer Science 3541, p. 278, ISBN 978-3-540-26306-7

\bibitem{GIST09} Douze M., Jégou H., Sandhawalia H., Amsaleg L, Schmid C.,\emph{Evaluation of GIST descriptors for web-scale image search}, Proceedings of the ACM International Conference on Image and Video Retrieval (CIVR '09). ACM, New York, 2009

\bibitem{EPSTEIN00} Epstein R., Stanley D., Harris A., Kanwisher N., \emph{The parahippocampal place area: Perception, encoding, or memory retrieval?}, Neuron, vol. 23, pp. 115 – 125, 2000

\bibitem{FREUND97} Freund Y., Schapire R.E., \emph{A Decision-Theoretic Generalization of On-Line Learning and an Application to Boosting}, Journal of Computer and System Sciences, Volume 55, Issue 1, August 1997, Pages 119–139

\bibitem{FUKUNAGA90} Fukunaga K., \emph{Introduction to Statistical Pattern Recognition}, Academic Press, 1990, ISBN 9780080478654

\bibitem{GLAZER08} Glazer A., Sipper M., \emph{Evolving an Automatic Defect Classification Tool}, Applications of Evolutionary Computing, Heidelberg: Springer, 2008, Pages 194-203

\bibitem{GONZALES01} Gonzales R. C., Woods R. E., \emph{Digital Image Processing}, Boston MA, USA: Addison-Wesley Longman Publishing, 2001, ISBN 0201180758

\bibitem{GMM10} Górriz J. M., Segovia F., Ramírez J., Lassl A., Salas-Gonzalez D., \emph{GMM based SPECT image classification for the diagnosis of Alzheimer’s disease}, Applied Soft Computing, Volume 11, Issue 2, March 2011, Pages 2313-2325, ISSN 1568-4946

\bibitem{GRAY18} Gray H., \emph{Anatomy of the Human Body}, Philadelphia: Lea \& Febiger, 1918 

\bibitem{HEIKKILA04} Heikkilä M., Pietikäinen M., Heikkilä J., \emph{A texture-based method for detecting moving objects}, 15th British Machine Vision Conference (BMVC), pages 187–196, London, UK, 2004

\bibitem{HAND01} Hand D., Mannila H. Smyth P., \emph{Eksploracja danych}, Warszawa: Wydawnictwo Naukowo-Techniczne, 2005, ISBN 83-204-3053-4

\bibitem{HERING64} Hering E, \emph{Outlines of a Theory of the Light Sense}, Harvard University Press, Cambridge, 1964

\bibitem{HEUSCH06} Heusch G., Rodriguez Y., Marcel S., \emph{Local binary patterns as an image preprocessing for face authentication}, Automatic Face and Gesture Recognition, 2006, Pages 6-14

\bibitem{HUANG11} Huang Y., Liu Q., Lv F., Gong Y., Dimitris N., \emph{Unsupervised Image Categorization by Hypergraph Partition}, Pattern Analysis and Machine Intelligence, IEEE Transactions, Volume 33, Issue 6, Pages 1266 - 1273

\bibitem{IMAGGA} Imagga APIs Documentation, http://docs.imagga.apiary.io/ [dostęp: 12.08.2014]

\bibitem{JUST06} Just A., Rodriguez Y., Marcel S., \emph{Hand posture classification and recognition using the modified census transform} AFGR, Southampton, UK, April 10-12 2006

\bibitem{KEGL09} Kégl B., \emph{Introduction to AdaBoost}, November 15, 2009, https://users.lal.in2p3.fr/kegl/teaching/stages/notes/tutorial.pdf [dostęp: 23.09.2014]

\bibitem{KOHAVI98} Kohavi R., Provost F., \emph{Glossary of terms, Machine Learning}, Vol. 30, No. 2/3, 1998, pp. 271-274

\bibitem{LINDENBERG90} Lindeberg T., \emph{Scale-space for discrete signals}, PAMI, 12(3), 1990, Pages 234–254

\bibitem{LZLM06} Liu Y., Zhang D., Lu G., Ma W-Y., \emph{A survey of content-based image retrieval with high-level semantics}, Pattern Recognition, Volume 40, Issue 1, January 2007, Pages 262-282, ISSN 0031-3203

\bibitem{MATURANA09} Maturana D., Mery D., Soto A., \emph{Face Recognition with Local Binary Patterns, Spatial Pyramid Histograms and Naive Bayes Nearest Neighbor classification}, SCCC, 2009, Pages 125-132

\bibitem{MELE06} Mele K., Maver J., Sue D., \emph{Image Categorization Using Local Probabilistic Descriptors}, Pattern Recognition, 2006. ICPR 2006. 18th International Conference on  (Volume:2 ), Pages 336 - 340

\bibitem{MONTEJO13} Montejo L.D., Jia J., Kim H. K., Netz U. J., Blaschke S., Müller G. A., Hielscher A. H., \emph{Computer-aided diagnosis of rheumatoid arthritis with optical tomography, Part 2: image classification}, Journal of biomedical optics, Volume 18, Jul 2013, ISSN 1560-2281

\bibitem{MORZY13} Morzy T., \emph{Eksploracja danych}, PWN, 2013, ISBN 978-83-01-17175-9

\bibitem{NEUBECK06} Neubeck A., Van Gool L., \emph{Efficient non-maximum suppression}, ICPR, 2006

\bibitem{LEUNG00} Leung T., Malik J., \emph{Representing and Recognizing the Visual Appearance of Materials using Three-dimensional Textons},International Journal of Computer Vision, Volume 43 Issue 1, June 2001, Pages 29 - 44 

\bibitem{MOTODA98} Liu H., Motoda H., \emph{Feature Selection for Knowledge Discovery Data Mining}, Boston: Kluwer Academic Publishers, 1998

\bibitem{LOWE04} Lowe D. G., \emph{Distinctive Image Features from Scale-Invariant Keypoints}, International Journal of Computer Vision, Volume 60, Issue 2, November 2004, Pages 91 - 110 

\bibitem{SIFT99} Lowe D. G., \emph{Object Recognition from Local Scale-Invariant Features}, Proceedings of the International Conference on Computer Vision-Volume 2 - Volume 2 (ICCV '99), Vol. 2. IEEE Computer Society, 1999, Page 1150

\bibitem{LUO11} Luo H-L., Wei H., Hu F-X., \emph{Improvements in image categorization using codebook ensembles}, Image and Vision Computing, Volume 29, Issue 11, October 2011, Pages 759–773

\bibitem{OJALA94} Ojala T., Pietikäinen M., Harwood D., \emph{A comparative study of texture measures with classification based on featured distributions}, Pattern Recognition, 29(1), 1996, Pages 51–59

\bibitem{OJALA02} Ojala T., Pietikäinen M, Mäenpää T. \emph{Multiresolution gray-scale and rotation invariant texture classification with local binary patterns}, IEEE Trans. on Pattern Analysis and Machine Intelligence, 24(7), Pages 971–987, 2002

\bibitem{OLIVA05} Oliva A., \emph{Gist of the scene}, Neurobiology of attention 696.64, 2005, Pages 251-258.

\bibitem{OLIVA-SCHYNS00} Oliva A., Schyns P., \emph{Colored diagnostic blobs mediate scene recognition}, Cognitive Psychology, vol. 41, pp. 176 – 210, 2000

\bibitem{OLIVA06} Oliva A., Torralba A., \emph{Building the gist of a scene: the role of global image features in recognition}, Progress in Brain Research, Vol. 155, 2006, Pages 23-36

\bibitem{OLIVA00} Oliva A., Torralba A., \emph{Modeling the Shape of the Scene: A Holistic Representation of the Spatial Envelope}, International Journal of Computer Vision, May 2001, Volume 42, Issue 3, pp 145-175

\bibitem{PIXIT} PiXiT, http://www.montefiore.ulg.ac.be/~maree/pixit.html [dostęp: 12.08.2014]

\bibitem{PLATT00} Platt J.C., Cristianini N., Shawe-taylor J., \emph{Large Margin DAGs for Multiclass Classification}, Advances in Neural Information Processing Systems, MIT Press, 2000, Pages 547-553

\bibitem{POTTER76} Potter M. C., \emph{Short-term conceptual memory for pictures}, Journal of Experimental Psychology: Human Learning and Memory, 1976, Pages 509–522

\bibitem{SCHWEIGER09} Schweiger F., Zeisl B., Georgel P et al.: Maximum Detector Response Markers for SIFT and SURF, VMV, 
2009

\bibitem{SCHYNS94} Schyns P.G., Oliva A., \emph{From blobs to boundary edges: evidence for time- and spatial-scale-dependent scene} recognition, 1994, Psychol. Sci., 5, Pages 195–200

\bibitem{SIAGIAN07} Siagian C., Itti L., \emph{Rapid biologically-inspired scene classi cation using features shared with visual attention}, IEEE Transactions on Pattern Analysis and Machine Intelligence, v. 29, no. 2, pp. 300–312, Feb 2007

\bibitem{Google2010} Smith N., \emph{Ooh! Ahh! Google Images presents a nicer way to surf the visual web}, Google Official Blog, 2010, http://googleblog.blogspot.com/2010/07/ooh-ahh-google-images-presents-nicer.html [dostęp: 05.08.2014]

\bibitem{STRUMIL} Strumillo P., \emph{Przetwarzanie obrazów, wykłady}, http://www.eletel.p.lodz.pl/pstrumil/ [dostęp: 6.09.2014]

\bibitem{SUVDAA2012} Suvdaa B., Ahn J., Ko J., \emph{Steel Surface Defects Detection and Classification Using SIFT and Voting Strategy}, International Journal of Software Engineering and Its Applications, Volume 6, No. 2, Apri 2012, Pages 161-166

\bibitem{Tad91} Tadeusiewicz R., Flasiński M., \emph{Rozpoznawanie obrazów}, Warszawa: Państwowe Wydawnictwo Naukowe, 1991, ISBN 83-01-10558-5

\bibitem{THORPE95} Thorpe S., Fize D., Marlot C., \emph{Speed of processing in the human visual system}, Nature, vol. 381, pp. 520 – 522, 1995

\bibitem{WARWICK10} Wernick M.N., Yongyi Y., Brankov J.G., Yourganov G., Strother S.C., \emph{Machine Learning in Medical Imaging}, Signal Processing Magazine, IEEE, Volume 27,  Issue 4, July 2010, Pages 25-38

\bibitem{WOLTER07} Wolter M., Zemła A., \emph{Optimization of tau identification in ATLAS experiment using multivariate tools}, ACAT 2007, http://cds.cern.ch/record/1027582/files/slide-2007-017.pdf [dostęp: 23.09.2014]

\bibitem{VALPOLA} Valpola H., \emph{Bayesian Ensemble Learning for Nonlinear Factor Analysis}, Acta Polytechnica Scandinavica, Mathematics and Computing Series No. 108, Espoo 2000, 54 pp.

\bibitem{VISWANATHAN08}  Viswanathan M., Siagian C., Itti L., \emph{Comparisons of Gist Models in Rapid Scene Categorization Tasks}, 2008

\bibitem{Vitaladevuni13} Vitaladevuni S.N., Natarajan P. ; Shuang W., Xiaodan Z., Prasad R. , Natarajan P., \emph{Scene image categorization and video event detection using Naive Bayes Nearest Neighbor}, Applications of Computer Vision (WACV), 2013 IEEE Workshop on, 2013, Pages 140 - 147

\bibitem{YAMAUCHI11} Yamauchi Y., Matsushima C., Yamashita T., Fujiyoshi H., \emph{Relational HOG feature with wild-card for object detection}, ICCV 2011, 6-13 Nov. 2011, Pages 1785 - 1792
 
\end{thebibliography} 